Metrics

### 2023-12-11 src/plots.Rmd
Fix exploration cod plot labels

# Format plot data
ecoddata <- df %>%
    filter(is_agreed == TRUE) %>%
    group_by(physician_cghr10) %>%
    summarize(count = n()) %>%
    mutate(
        cod_label = paste0(
            physician_cghr10,
            "\n(n=", count, ", ",
            if_else(
                ((count / nagree) * 100) < 1,
                "<1",
                as.character(round((count / nagree) * 100))
            ), "%)"
        )
    ) %>%
    arrange(count) %>%
    mutate(
        cod_label = factor(cod_label, levels = unique(cod_label))
    )

>>>>

# Format plot data
ecoddata <- df %>%
    filter(is_agreed == TRUE) %>%
    group_by(physician_cghr10) %>%
    summarize(count = n()) %>%
    mutate(
        cod_label = paste0(
            if_else(
                str_count(physician_cghr10, "\\s+") > 3,
                str_replace(physician_cghr10, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n"),
                physician_cghr10
            ),
            "\n(n=", count, ", ",
            if_else(
                ((count / nagree) * 100) < 1,
                "<1",
                as.character(round((count / nagree) * 100))
            ), "%)"
        )
    ) %>%
    arrange(count) %>%
    mutate(
        cod_label = factor(cod_label, levels = unique(cod_label))
    )
